Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-10 eswc-2012/phdsymp.tex
benchmarking sota
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@52 43ef1190-90fd-4dd7-a769-d0121f02b80e

The problems addressed by these studies are almost orthogonal to the
problems considered by my proposed project.

>>>>

The problems addressed by these studies are almost orthogonal to the
problems considered by my proposed project. I have not to date seen
any work towards using contemporary statistical methods to evaluate
the performance of software, but I shall admit that my literature
study have been limited to RDF/OWL databases, and practical benchmarks
of databases, file systems, scientific software, etc. Thus, the
existence of relevant references in the deeper computer science
literature is a key issue I would appreciate discussing at the
Symposium.
